`r params$doc_title`

### 2023-03-02 scripts/MSc.Rmd
updated plots and performance measures for all 10 methods

## for performance measures later
# retrieve IVW/ MODE/ CONMIX cols for BMI -> GSD 
colname_IVW_theta_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "IVW_theta_sim_BMI_GSD_")]
colname_IVW_theta_se_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "IVW_theta_se_sim_BMI_GSD_")]
colname_MODE_theta_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "MODE_theta_sim_BMI_GSD_")]
colname_MODE_theta_se_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "MODE_theta_se_sim_BMI_GSD_")]
colname_CONMIX_theta_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "CONMIX_theta_sim_BMI_GSD_")]
colname_CONMIX_theta_se_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "CONMIX_theta_se_sim_BMI_GSD_")]
colname_MRMIX_theta_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "MRMIX_theta_sim_BMI_GSD_")]
colname_MRMIX_theta_se_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "MRMIX_theta_se_sim_BMI_GSD_")]
# retrieve IVW/ MODE/ CONMIX cols for BMI -> GBC
# removed on 2023-01-24 (see github)

@@

## get performance metrics    # https://stackoverflow.com/questions/47415072/pass-multiple-functions-to-purrrmap
funs <- c(mean = mean, emp_se=emp_se, bias = bias, mse = mse)
## args gsd
args.gsd.ivw <- list(theta = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == "IVW"], 
                     nsim=nrow(est_sim)
                     ) # trim argument non-matching and ignored for median
args.gsd.mode <- list(theta = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == "mode"], 
                     nsim=nrow(est_sim)
                     )
args.gsd.conmix <- list(theta = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == "conmix"], 
                     nsim=nrow(est_sim)
                     )
args.gsd.mrmix <- list(theta = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == "MRMix"], 
                     nsim=nrow(est_sim)
                     )
## args gbc
#deleted 2023-01-29

@@

```{r CALC-perf-metrics-GSD}
IVW_GSD_performance_metrics <- est_sim %>% 
  select(!!!(colname_IVW_theta_sim_BMI_GSD)) %>% 
  map_df(.f = ~ funs %>% 
           map(exec, .x, !!!args.gsd.ivw), .id = "var") %>% 
  cbind(sample_size_filtered) %>% 
  rename(N = sample_size_filtered)

MODE_GSD_performance_metrics <- est_sim %>% 
  select(!!!(colname_MODE_theta_sim_BMI_GSD)) %>% 
  map_df(.f = ~ funs %>% 
           map(exec, .x, !!!args.gsd.mode), .id = "var") %>% 
  cbind(sample_size_filtered) %>% 
  rename(N = sample_size_filtered)

CONMIX_GSD_performance_metrics <- est_sim %>% 
  select(!!!(colname_CONMIX_theta_sim_BMI_GSD)) %>% 
  map_df(.f = ~ funs %>% 
           map(exec, .x, !!!args.gsd.conmix), .id = "var") %>% 
  cbind(sample_size_filtered) %>% 
  rename(N = sample_size_filtered)

MRMIX_GSD_performance_metrics <- est_sim %>% 
  select(!!!(colname_MRMIX_theta_sim_BMI_GSD)) %>% 
  map_df(.f = ~ funs %>% 
           map(exec, .x, !!!args.gsd.conmix), .id = "var") %>% 
  cbind(sample_size_filtered) %>% 
  rename(N = sample_size_filtered)
```

@@

# GSD
IVW_GSD_coverage_calc <- c()
IVW_GSD_coverage_bias_eliminated_calc <- c()
IVW_GSD_type1error_calc <- c()
MODE_GSD_coverage_calc <- c()
MODE_GSD_coverage_bias_eliminated_calc <- c()
MODE_GSD_type1error_calc <- c()
CONMIX_GSD_coverage_calc <- c()
CONMIX_GSD_coverage_bias_eliminated_calc <- c()
CONMIX_GSD_type1error_calc <- c()
MRMIX_GSD_coverage_calc <- c()
MRMIX_GSD_coverage_bias_eliminated_calc <- c()
MRMIX_GSD_type1error_calc <- c()
# GBC
## deleted 2023-01-29

@@

@@

```{r add-additional-metrics-to-df-and-print-GSD}
## GSD --------------------------
IVW_GSD_performance_metrics <- IVW_GSD_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(IVW_GSD_coverage_calc, IVW_GSD_coverage_bias_eliminated_calc, IVW_GSD_type1error_calc)) %>% 
  rename(coverage = IVW_GSD_coverage_calc, 
         coverage_bias_eliminated = IVW_GSD_coverage_bias_eliminated_calc, 
         type1error = IVW_GSD_type1error_calc) %>% 
  as_tibble()
IVW_GSD_performance_metrics %>% 
  mutate(across(cols = where(is.numeric), round(3))) %>% 
  kable(caption = "IVW method on BMI -> GSD performance metrics") %>% 
  kable_styling(font_size=10)

MODE_GSD_performance_metrics <- MODE_GSD_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(MODE_GSD_coverage_calc, 
                   MODE_GSD_coverage_bias_eliminated_calc, MODE_GSD_type1error_calc)) %>% 
  rename(coverage = MODE_GSD_coverage_calc, 
         coverage_bias_eliminated = MODE_GSD_coverage_bias_eliminated_calc, 
         type1error = MODE_GSD_type1error_calc) %>% 
  as_tibble()
MODE_GSD_performance_metrics %>% 
  mutate(across(cols = where(is.numeric), round(3))) %>% 
  kable(caption = "MODE method on BMI -> GSD performance metrics") %>% 
  kable_styling(font_size=10)

CONMIX_GSD_performance_metrics <- CONMIX_GSD_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(CONMIX_GSD_coverage_calc, 
                   CONMIX_GSD_coverage_bias_eliminated_calc, CONMIX_GSD_type1error_calc)) %>% 
  rename(coverage = CONMIX_GSD_coverage_calc, 
         coverage_bias_eliminated = CONMIX_GSD_coverage_bias_eliminated_calc, 
         type1error = CONMIX_GSD_type1error_calc) %>% 
  as_tibble()
CONMIX_GSD_performance_metrics %>% 
  mutate(across(cols = where(is.numeric), round(3))) %>% 
  kable(caption = "CONMIX method on BMI -> GSD performance metrics") %>% 
  kable_styling(font_size=10)

MRMIX_GSD_performance_metrics <- MRMIX_GSD_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(MRMIX_GSD_coverage_calc, 
                   MRMIX_GSD_coverage_bias_eliminated_calc, MRMIX_GSD_type1error_calc)) %>% 
  rename(coverage = MRMIX_GSD_coverage_calc, 
         coverage_bias_eliminated = MRMIX_GSD_coverage_bias_eliminated_calc, 
         type1error = MRMIX_GSD_type1error_calc) %>% 
  as_tibble()
MRMIX_GSD_performance_metrics %>% 
  mutate(across(cols = where(is.numeric), round(3))) %>% 
  kable(caption = "MRMIX method on BMI -> GSD performance metrics") %>% 
  kable_styling(font_size=10)
```

```{r store-performance-metrics-csv}
## GSD
filename_IVW_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
                                               Sys.Date(), "_IVW_GSD_performance_metrics_NSIM_", nsim, ".csv")
filename_MODE_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
                                               Sys.Date(), "_MODE_GSD_performance_metrics_NSIM_", nsim, ".csv")
filename_CONMIX_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
                                               Sys.Date(), "_CONMIX_GSD_performance_metrics_NSIM_", nsim, ".csv")
filename_MRMIX_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
                                               Sys.Date(), "_MRMIX_GSD_performance_metrics_NSIM_", nsim, ".csv")
write.csv2(x = IVW_GSD_performance_metrics, file = filename_IVW_GSD_performance_metrics)
write.csv2(x = MODE_GSD_performance_metrics, file = filename_MODE_GSD_performance_metrics)
write.csv2(x = CONMIX_GSD_performance_metrics, file = filename_CONMIX_GSD_performance_metrics)
write.csv2(x = MRMIX_GSD_performance_metrics, file = filename_MRMIX_GSD_performance_metrics)
```

>>>>

## for performance measures later
# retrieve IVW/ MODE/ CONMIX/... cols for BMI -> GSD 
#1
colname_IVW_theta_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "IVW_theta_sim_BMI_GSD_")]
colname_IVW_theta_se_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "IVW_theta_se_sim_BMI_GSD_")]
#2
colname_MODE_theta_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "MODE_theta_sim_BMI_GSD_")]
colname_MODE_theta_se_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "MODE_theta_se_sim_BMI_GSD_")]
#3
colname_CONMIX_theta_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "CONMIX_theta_sim_BMI_GSD_")]
colname_CONMIX_theta_se_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "CONMIX_theta_se_sim_BMI_GSD_")]
#4
colname_MRMIX_theta_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "MRMIX_theta_sim_BMI_GSD_")]
colname_MRMIX_theta_se_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "MRMIX_theta_se_sim_BMI_GSD_")]
#5
colname_MEDIAN_theta_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "MEDIAN_theta_sim_BMI_GSD_")]
colname_MEDIAN_theta_se_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "MEDIAN_theta_se_sim_BMI_GSD_")]
#6
colname_EGGER_theta_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "EGGER_theta_sim_BMI_GSD_")]
colname_EGGER_theta_se_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "EGGER_theta_se_sim_BMI_GSD_")]
#7
colname_ROBUST_theta_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "ROBUST_theta_sim_BMI_GSD_")]
colname_ROBUST_theta_se_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "ROBUST_theta_se_sim_BMI_GSD_")]
#8
colname_PRESSO_theta_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "PRESSO_theta_sim_BMI_GSD_")]
colname_PRESSO_theta_se_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "PRESSO_theta_se_sim_BMI_GSD_")]
#9
colname_RAPS_theta_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "RAPS_theta_sim_BMI_GSD_")]
colname_RAPS_theta_se_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "RAPS_theta_se_sim_BMI_GSD_")]
#10
colname_LASSO_theta_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "LASSO_theta_sim_BMI_GSD_")]
colname_LASSO_theta_se_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "LASSO_theta_se_sim_BMI_GSD_")]

# retrieve IVW/ MODE/ CONMIX cols for BMI -> GBC
# removed on 2023-01-24 (see github)

@@

## get performance metrics    # https://stackoverflow.com/questions/47415072/pass-multiple-functions-to-purrrmap
funs <- c(mean = mean, emp_se=emp_se, bias = bias, mse = mse)
## args gsd
#1
args.gsd.ivw <- list(theta = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == "IVW"], 
                     nsim=nrow(est_sim)
                     ) # trim argument non-matching and ignored for median
#2
args.gsd.mode <- list(theta = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == "mode"], 
                     nsim=nrow(est_sim)
                     )
#3
args.gsd.conmix <- list(theta = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == "conmix"], 
                     nsim=nrow(est_sim)
                     )
#4
args.gsd.mrmix <- list(theta = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == "MRMix"], 
                     nsim=nrow(est_sim)
                     )
#5
args.gsd.median <- list(theta = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == "median"], 
                     nsim=nrow(est_sim)
                     )
#6
args.gsd.egger <- list(theta = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == "egger"], 
                     nsim=nrow(est_sim)
                     )
#7
args.gsd.robust <- list(theta = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == "Robust"], 
                     nsim=nrow(est_sim)
                     )
#8
args.gsd.presso <- list(theta = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == "PRESSO"], 
                     nsim=nrow(est_sim)
                     )
#9
args.gsd.raps <- list(theta = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == "RAPS"], 
                     nsim=nrow(est_sim)
                     )
#10
args.gsd.lasso <- list(theta = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == "Lasso"], 
                     nsim=nrow(est_sim)
                     )
## args gbc
#deleted 2023-01-29

@@

```{r CALC-perf-metrics-GSD}
#1
IVW_GSD_performance_metrics <- est_sim %>% 
  select(!!!(colname_IVW_theta_sim_BMI_GSD)) %>% 
  map_df(.f = ~ funs %>% 
           map(exec, .x, !!!args.gsd.ivw), .id = "var") %>% 
  cbind(sample_size_filtered) %>% 
  rename(N = sample_size_filtered)
#2
MODE_GSD_performance_metrics <- est_sim %>% 
  select(!!!(colname_MODE_theta_sim_BMI_GSD)) %>% 
  map_df(.f = ~ funs %>% 
           map(exec, .x, !!!args.gsd.mode), .id = "var") %>% 
  cbind(sample_size_filtered) %>% 
  rename(N = sample_size_filtered)
#3
CONMIX_GSD_performance_metrics <- est_sim %>% 
  select(!!!(colname_CONMIX_theta_sim_BMI_GSD)) %>% 
  map_df(.f = ~ funs %>% 
           map(exec, .x, !!!args.gsd.conmix), .id = "var") %>% 
  cbind(sample_size_filtered) %>% 
  rename(N = sample_size_filtered)
#4
MRMIX_GSD_performance_metrics <- est_sim %>% 
  select(!!!(colname_MRMIX_theta_sim_BMI_GSD)) %>% 
  map_df(.f = ~ funs %>% 
           map(exec, .x, !!!args.gsd.mrmix), .id = "var") %>% 
  cbind(sample_size_filtered) %>% 
  rename(N = sample_size_filtered)
#5
MEDIAN_GSD_performance_metrics <- est_sim %>% 
  select(!!!(colname_MEDIAN_theta_sim_BMI_GSD)) %>% 
  map_df(.f = ~ funs %>% 
           map(exec, .x, !!!args.gsd.median), .id = "var") %>% 
  cbind(sample_size_filtered) %>% 
  rename(N = sample_size_filtered)
#6
EGGER_GSD_performance_metrics <- est_sim %>% 
  select(!!!(colname_EGGER_theta_sim_BMI_GSD)) %>% 
  map_df(.f = ~ funs %>% 
           map(exec, .x, !!!args.gsd.egger), .id = "var") %>% 
  cbind(sample_size_filtered) %>% 
  rename(N = sample_size_filtered)
#7
ROBUST_GSD_performance_metrics <- est_sim %>% 
  select(!!!(colname_ROBUST_theta_sim_BMI_GSD)) %>% 
  map_df(.f = ~ funs %>% 
           map(exec, .x, !!!args.gsd.robust), .id = "var") %>% 
  cbind(sample_size_filtered) %>% 
  rename(N = sample_size_filtered)
#8
PRESSO_GSD_performance_metrics <- est_sim %>% 
  select(!!!(colname_PRESSO_theta_sim_BMI_GSD)) %>% 
  map_df(.f = ~ funs %>% 
           map(exec, .x, !!!args.gsd.presso), .id = "var") %>% 
  cbind(sample_size_filtered) %>% 
  rename(N = sample_size_filtered)
#9
RAPS_GSD_performance_metrics <- est_sim %>% 
  select(!!!(colname_RAPS_theta_sim_BMI_GSD)) %>% 
  map_df(.f = ~ funs %>% 
           map(exec, .x, !!!args.gsd.raps), .id = "var") %>% 
  cbind(sample_size_filtered) %>% 
  rename(N = sample_size_filtered)
#10
LASSO_GSD_performance_metrics <- est_sim %>% 
  select(!!!(colname_LASSO_theta_sim_BMI_GSD)) %>% 
  map_df(.f = ~ funs %>% 
           map(exec, .x, !!!args.gsd.lasso), .id = "var") %>% 
  cbind(sample_size_filtered) %>% 
  rename(N = sample_size_filtered)
```

@@

# GSD
#1
IVW_GSD_coverage_calc <- c()
IVW_GSD_coverage_bias_eliminated_calc <- c()
IVW_GSD_type1error_calc <- c()
#2
MODE_GSD_coverage_calc <- c()
MODE_GSD_coverage_bias_eliminated_calc <- c()
MODE_GSD_type1error_calc <- c()
#3
CONMIX_GSD_coverage_calc <- c()
CONMIX_GSD_coverage_bias_eliminated_calc <- c()
CONMIX_GSD_type1error_calc <- c()
#4
MRMIX_GSD_coverage_calc <- c()
MRMIX_GSD_coverage_bias_eliminated_calc <- c()
MRMIX_GSD_type1error_calc <- c()
#5
MEDIAN_GSD_coverage_calc <- c()
MEDIAN_GSD_coverage_bias_eliminated_calc <- c()
MEDIAN_GSD_type1error_calc <- c()
#6
EGGER_GSD_coverage_calc <- c()
EGGER_GSD_coverage_bias_eliminated_calc <- c()
EGGER_GSD_type1error_calc <- c()
#7
ROBUST_GSD_coverage_calc <- c()
ROBUST_GSD_coverage_bias_eliminated_calc <- c()
ROBUST_GSD_type1error_calc <- c()
#8
PRESSO_GSD_coverage_calc <- c()
PRESSO_GSD_coverage_bias_eliminated_calc <- c()
PRESSO_GSD_type1error_calc <- c()
#9
RAPS_GSD_coverage_calc <- c()
RAPS_GSD_coverage_bias_eliminated_calc <- c()
RAPS_GSD_type1error_calc <- c()
#10
LASSO_GSD_coverage_calc <- c()
LASSO_GSD_coverage_bias_eliminated_calc <- c()
LASSO_GSD_type1error_calc <- c()

@@

  ## 5/ MEDIAN
  col_MEDIAN_GSD_theta <- paste0("MEDIAN_theta_sim_BMI_GSD_", format(sample_size, scientific = FALSE))
  col_MEDIAN_GSD_theta_se <- paste0("MEDIAN_theta_se_sim_BMI_GSD_", format(sample_size, scientific = FALSE))
  col_MEDIAN_GSD_mr_pval <- paste0("MEDIAN_mr_pval_BMI_GSD_", format(sample_size, scientific = FALSE))
  MEDIAN_GSD_coverage_calc[i] <- coverage(thetaobs = est_sim[col_MEDIAN_GSD_theta], 
                                       thetaobs_se = est_sim[col_MEDIAN_GSD_theta_se], 
                                       theta = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == "median"])
  MEDIAN_GSD_coverage_bias_eliminated_calc[i] <- coverage_bias_eliminated(thetaobs = est_sim[[col_MEDIAN_GSD_theta]], 
                                                                       thetaobs_se = est_sim[[col_MEDIAN_GSD_theta_se]])
  MEDIAN_GSD_type1error_calc[i] <- type1error(est_sim[[col_MEDIAN_GSD_mr_pval]])
  ## 6/ EGGER
  col_EGGER_GSD_theta <- paste0("EGGER_theta_sim_BMI_GSD_", format(sample_size, scientific = FALSE))
  col_EGGER_GSD_theta_se <- paste0("EGGER_theta_se_sim_BMI_GSD_", format(sample_size, scientific = FALSE))
  col_EGGER_GSD_mr_pval <- paste0("EGGER_mr_pval_BMI_GSD_", format(sample_size, scientific = FALSE))
  EGGER_GSD_coverage_calc[i] <- coverage(thetaobs = est_sim[col_EGGER_GSD_theta], 
                                       thetaobs_se = est_sim[col_EGGER_GSD_theta_se], 
                                       theta = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == "egger"])
  EGGER_GSD_coverage_bias_eliminated_calc[i] <- coverage_bias_eliminated(thetaobs = est_sim[[col_EGGER_GSD_theta]], 
                                                                       thetaobs_se = est_sim[[col_EGGER_GSD_theta_se]])
  EGGER_GSD_type1error_calc[i] <- type1error(est_sim[[col_EGGER_GSD_mr_pval]])  
  ## 7/ ROBUST
  col_ROBUST_GSD_theta <- paste0("ROBUST_theta_sim_BMI_GSD_", format(sample_size, scientific = FALSE))
  col_ROBUST_GSD_theta_se <- paste0("ROBUST_theta_se_sim_BMI_GSD_", format(sample_size, scientific = FALSE))
  col_ROBUST_GSD_mr_pval <- paste0("ROBUST_mr_pval_BMI_GSD_", format(sample_size, scientific = FALSE))
  ROBUST_GSD_coverage_calc[i] <- coverage(thetaobs = est_sim[col_ROBUST_GSD_theta], 
                                       thetaobs_se = est_sim[col_ROBUST_GSD_theta_se], 
                                       theta = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == "Robust"])
  ROBUST_GSD_coverage_bias_eliminated_calc[i] <- coverage_bias_eliminated(thetaobs = est_sim[[col_ROBUST_GSD_theta]], 
                                                                       thetaobs_se = est_sim[[col_ROBUST_GSD_theta_se]])
  ROBUST_GSD_type1error_calc[i] <- type1error(est_sim[[col_ROBUST_GSD_mr_pval]])  
  ## 8/ PRESSO
  col_PRESSO_GSD_theta <- paste0("PRESSO_theta_sim_BMI_GSD_", format(sample_size, scientific = FALSE))
  col_PRESSO_GSD_theta_se <- paste0("PRESSO_theta_se_sim_BMI_GSD_", format(sample_size, scientific = FALSE))
  col_PRESSO_GSD_mr_pval <- paste0("PRESSO_mr_pval_BMI_GSD_", format(sample_size, scientific = FALSE))
  PRESSO_GSD_coverage_calc[i] <- coverage(thetaobs = est_sim[col_PRESSO_GSD_theta], 
                                       thetaobs_se = est_sim[col_PRESSO_GSD_theta_se], 
                                       theta = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == "PRESSO"])
  PRESSO_GSD_coverage_bias_eliminated_calc[i] <- coverage_bias_eliminated(thetaobs = est_sim[[col_PRESSO_GSD_theta]], 
                                                                       thetaobs_se = est_sim[[col_PRESSO_GSD_theta_se]])
  PRESSO_GSD_type1error_calc[i] <- type1error(est_sim[[col_PRESSO_GSD_mr_pval]])
  ## 9/ RAPS
  col_RAPS_GSD_theta <- paste0("RAPS_theta_sim_BMI_GSD_", format(sample_size, scientific = FALSE))
  col_RAPS_GSD_theta_se <- paste0("RAPS_theta_se_sim_BMI_GSD_", format(sample_size, scientific = FALSE))
  col_RAPS_GSD_mr_pval <- paste0("RAPS_mr_pval_BMI_GSD_", format(sample_size, scientific = FALSE))
  RAPS_GSD_coverage_calc[i] <- coverage(thetaobs = est_sim[col_RAPS_GSD_theta], 
                                       thetaobs_se = est_sim[col_RAPS_GSD_theta_se], 
                                       theta = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == "RAPS"])
  RAPS_GSD_coverage_bias_eliminated_calc[i] <- coverage_bias_eliminated(thetaobs = est_sim[[col_RAPS_GSD_theta]], 
                                                                       thetaobs_se = est_sim[[col_RAPS_GSD_theta_se]])
  RAPS_GSD_type1error_calc[i] <- type1error(est_sim[[col_RAPS_GSD_mr_pval]])  
  ## 10/ LASSO
  col_LASSO_GSD_theta <- paste0("LASSO_theta_sim_BMI_GSD_", format(sample_size, scientific = FALSE))
  col_LASSO_GSD_theta_se <- paste0("LASSO_theta_se_sim_BMI_GSD_", format(sample_size, scientific = FALSE))
  col_LASSO_GSD_mr_pval <- paste0("LASSO_mr_pval_BMI_GSD_", format(sample_size, scientific = FALSE))
  LASSO_GSD_coverage_calc[i] <- coverage(thetaobs = est_sim[col_LASSO_GSD_theta], 
                                       thetaobs_se = est_sim[col_LASSO_GSD_theta_se], 
                                       theta = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == "Lasso"])
  LASSO_GSD_coverage_bias_eliminated_calc[i] <- coverage_bias_eliminated(thetaobs = est_sim[[col_LASSO_GSD_theta]], 
                                                                       thetaobs_se = est_sim[[col_LASSO_GSD_theta_se]])
  LASSO_GSD_type1error_calc[i] <- type1error(est_sim[[col_LASSO_GSD_mr_pval]])  

@@

```{r add-additional-metrics-to-df-and-print-GSD}
## GSD --------------------------
#1
IVW_GSD_performance_metrics <- IVW_GSD_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(IVW_GSD_coverage_calc, IVW_GSD_coverage_bias_eliminated_calc, IVW_GSD_type1error_calc)) %>% 
  rename(coverage = IVW_GSD_coverage_calc, 
         coverage_bias_eliminated = IVW_GSD_coverage_bias_eliminated_calc, 
         type1error = IVW_GSD_type1error_calc) %>% 
  as_tibble()
IVW_GSD_performance_metrics %>% 
  mutate(across(cols = where(is.numeric), round(3))) %>% 
  kable(caption = "IVW method on BMI -> GSD performance metrics") %>% 
  kable_styling(font_size=10)
#2
MODE_GSD_performance_metrics <- MODE_GSD_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(MODE_GSD_coverage_calc, 
                   MODE_GSD_coverage_bias_eliminated_calc, MODE_GSD_type1error_calc)) %>% 
  rename(coverage = MODE_GSD_coverage_calc, 
         coverage_bias_eliminated = MODE_GSD_coverage_bias_eliminated_calc, 
         type1error = MODE_GSD_type1error_calc) %>% 
  as_tibble()
MODE_GSD_performance_metrics %>% 
  mutate(across(cols = where(is.numeric), round(3))) %>% 
  kable(caption = "MODE method on BMI -> GSD performance metrics") %>% 
  kable_styling(font_size=10)
#3
CONMIX_GSD_performance_metrics <- CONMIX_GSD_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(CONMIX_GSD_coverage_calc, 
                   CONMIX_GSD_coverage_bias_eliminated_calc, CONMIX_GSD_type1error_calc)) %>% 
  rename(coverage = CONMIX_GSD_coverage_calc, 
         coverage_bias_eliminated = CONMIX_GSD_coverage_bias_eliminated_calc, 
         type1error = CONMIX_GSD_type1error_calc) %>% 
  as_tibble()
CONMIX_GSD_performance_metrics %>% 
  mutate(across(cols = where(is.numeric), round(3))) %>% 
  kable(caption = "CONMIX method on BMI -> GSD performance metrics") %>% 
  kable_styling(font_size=10)
#4
MRMIX_GSD_performance_metrics <- MRMIX_GSD_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(MRMIX_GSD_coverage_calc, 
                   MRMIX_GSD_coverage_bias_eliminated_calc, MRMIX_GSD_type1error_calc)) %>% 
  rename(coverage = MRMIX_GSD_coverage_calc, 
         coverage_bias_eliminated = MRMIX_GSD_coverage_bias_eliminated_calc, 
         type1error = MRMIX_GSD_type1error_calc) %>% 
  as_tibble()
MRMIX_GSD_performance_metrics %>% 
  mutate(across(cols = where(is.numeric), round(3))) %>% 
  kable(caption = "MRMIX method on BMI -> GSD performance metrics") %>% 
  kable_styling(font_size=10)
#5
MEDIAN_GSD_performance_metrics <- MEDIAN_GSD_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(MEDIAN_GSD_coverage_calc, 
                   MEDIAN_GSD_coverage_bias_eliminated_calc, MEDIAN_GSD_type1error_calc)) %>% 
  rename(coverage = MEDIAN_GSD_coverage_calc, 
         coverage_bias_eliminated = MEDIAN_GSD_coverage_bias_eliminated_calc, 
         type1error = MEDIAN_GSD_type1error_calc) %>% 
  as_tibble()
MEDIAN_GSD_performance_metrics %>% 
  mutate(across(cols = where(is.numeric), round(3))) %>% 
  kable(caption = "MEDIAN method on BMI -> GSD performance metrics") %>% 
  kable_styling(font_size=10)
#6
EGGER_GSD_performance_metrics <- EGGER_GSD_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(EGGER_GSD_coverage_calc, 
                   EGGER_GSD_coverage_bias_eliminated_calc, EGGER_GSD_type1error_calc)) %>% 
  rename(coverage = EGGER_GSD_coverage_calc, 
         coverage_bias_eliminated = EGGER_GSD_coverage_bias_eliminated_calc, 
         type1error = EGGER_GSD_type1error_calc) %>% 
  as_tibble()
EGGER_GSD_performance_metrics %>% 
  mutate(across(cols = where(is.numeric), round(3))) %>% 
  kable(caption = "EGGER method on BMI -> GSD performance metrics") %>% 
  kable_styling(font_size=10)
#7
ROBUST_GSD_performance_metrics <- ROBUST_GSD_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(ROBUST_GSD_coverage_calc, 
                   ROBUST_GSD_coverage_bias_eliminated_calc, ROBUST_GSD_type1error_calc)) %>% 
  rename(coverage = ROBUST_GSD_coverage_calc, 
         coverage_bias_eliminated = ROBUST_GSD_coverage_bias_eliminated_calc, 
         type1error = ROBUST_GSD_type1error_calc) %>% 
  as_tibble()
ROBUST_GSD_performance_metrics %>% 
  mutate(across(cols = where(is.numeric), round(3))) %>% 
  kable(caption = "ROBUST method on BMI -> GSD performance metrics") %>% 
  kable_styling(font_size=10)
#8
PRESSO_GSD_performance_metrics <- PRESSO_GSD_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(PRESSO_GSD_coverage_calc, 
                   PRESSO_GSD_coverage_bias_eliminated_calc, PRESSO_GSD_type1error_calc)) %>% 
  rename(coverage = PRESSO_GSD_coverage_calc, 
         coverage_bias_eliminated = PRESSO_GSD_coverage_bias_eliminated_calc, 
         type1error = PRESSO_GSD_type1error_calc) %>% 
  as_tibble()
PRESSO_GSD_performance_metrics %>% 
  mutate(across(cols = where(is.numeric), round(3))) %>% 
  kable(caption = "PRESSO method on BMI -> GSD performance metrics") %>% 
  kable_styling(font_size=10)
#9
RAPS_GSD_performance_metrics <- RAPS_GSD_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(RAPS_GSD_coverage_calc, 
                   RAPS_GSD_coverage_bias_eliminated_calc, RAPS_GSD_type1error_calc)) %>% 
  rename(coverage = RAPS_GSD_coverage_calc, 
         coverage_bias_eliminated = RAPS_GSD_coverage_bias_eliminated_calc, 
         type1error = RAPS_GSD_type1error_calc) %>% 
  as_tibble()
RAPS_GSD_performance_metrics %>% 
  mutate(across(cols = where(is.numeric), round(3))) %>% 
  kable(caption = "RAPS method on BMI -> GSD performance metrics") %>% 
  kable_styling(font_size=10)
#10
LASSO_GSD_performance_metrics <- LASSO_GSD_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(LASSO_GSD_coverage_calc, 
                   LASSO_GSD_coverage_bias_eliminated_calc, LASSO_GSD_type1error_calc)) %>% 
  rename(coverage = LASSO_GSD_coverage_calc, 
         coverage_bias_eliminated = LASSO_GSD_coverage_bias_eliminated_calc, 
         type1error = LASSO_GSD_type1error_calc) %>% 
  as_tibble()
LASSO_GSD_performance_metrics %>% 
  mutate(across(cols = where(is.numeric), round(3))) %>% 
  kable(caption = "LASSO method on BMI -> GSD performance metrics") %>% 
  kable_styling(font_size=10)
